---
title: "Quiz 2"
author: "Le Wang"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```


1. Generate a vector called `x` that is a sequence number from $1$ to $9$.
$$
x = (1, 2, 3, 4, 5, 6, 7, 8, 9)
$$

```{r}
x <- 
```

2. Select and show what is the 3rd element of the vector $x$. 

```{r}

```

3. Select the numbers greater than $3$ in the vector $x$. Lets do it in two steps to help you understand the process

```{r}
# Step 1. Generate a vector of the same length, but with logical values (i.e., TRUE or FALSE) by 
# evaluating whether or not each element of x is greater than 3. Call this vector select

select <- 
select
  
# Step 2.   Put this vector with logical values to select the sub-vector of x. Call it subvector

subvector <- 
```

4. Using $x$ to construct the following matrix
$$
\begin{pmatrix}
1 & 2 & 3 \\
4 & 5 & 6 \\
7 & 8 & 9
\end{pmatrix}
$$


```{r}
matrix <- 
```


5. Give names to your matrix. 

$$
\begin{pmatrix}
 & \text{First} &  \text{Second} &  \text{Third} \\
\text{Katy} & 1 & 2 & 3 \\
\text{Hunter} & 4 & 5 & 6 \\
\text{Carson} & 7 & 8 & 9
\end{pmatrix}
$$

6. Use `R` to tell you what the respective dimensions of $x$ and $matrix$. 

```{r}
# dimension of x


# dimension of matrix


```

7. Create a data frame that looks like

$$
\begin{pmatrix}
 & \text{First} &  \text{Second} &  \text{Third} \\
 & 1 & 2 & 3 \\
 & 4 & 5 & 6 \\
\end{pmatrix}
$$

8. Create a tibble dataset that looks like the one above

